---
title: "How Covid-19 infected the Airbnb prices in Amsterdam, The Netherlands"
author: "Bram van den Bemt, Doga Bayraktar,Demi de Groot, Ellen van Berlo,Sam Messaoudi"
output: 
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r, echo = FALSE}
library(readr)
library(dplyr)
library(ggplot2)
```
# Introduction 
For the first step, the data extracted from the Airbnb site has been cleaned. Based on this clean data-set,the variables has been further reduced and a new variable has been added creating the  data-set only price district. The descriptions of the variables can be found below.As the initial step for the analysis, summary statistics for the data-set has been extracted, the results of this summary statistics is presented in the summary statistics CSV file. After, the data-frame has been visualized as mean plot, plotting districts by price difference. Results of the mean plot are presented in mean-plot pricedif district plot. After accounting for the outliers, a box plot has been plotted that can be found in boxplot pricedif district filtered plot.  Lastly, using the filtered dataset and checking the assumptions of the ANOVA analysis, the analysis (aov) has been ran and the results has been plotted as Tukey plot and a CSV file. The Tukey outputs can be found in tukey plot and tukey csv accordingly. 

## Variable Descriptions 

The cleaned data-set "../gen/temp/complete_price_comparison.csv" is composed of the variables:

#### ID 
ID variable is an integer variable. Represents the unique id of every listing.
#### Host ID
Host ID is an integer variable. Represents the unique id of the host that is holding the listing.
#### Neighbourhood Cleansed
Neighbourhood cleansed is a character variable. Represents the district that the listing is located. It has been reduced from 22 neighbourhoods of Amsterdam to 7 districts of Amsterdam.
#### Room type
Room type is a character variable. Represents the accommondation type of a listing. There is 4 room types in total.
#### Price 12.20
Price 12.20 is numeric variable. Represents the price of the accommondation per night in dollars in the month of December 2020.
#### Price 01.21
Price 01.21 is numeric variable. Represents the price of the accommondation per night in dollars in the month of January 2021.
#### Price 02.21
Price 02.21 is numeric variable. Represents the price of the accommondation per night in dollars in the month of February 2021.
#### Price 03.21
Price 03.21 is numeric variable. Represents the price of the accommondation per night in dollars in the month of March 2021.
#### Price 04.21
Price 04.21 is numeric variable. Represents the price of the accommondation per night in dollars in the month of April  2021.
#### Price 05.21
Price 05.21 is numeric variable. Represents the price of the accommondation per night in dollars in the month of May 2021.

With further coercion of the variables and an additional variable the dataframe has been reduced further into "../gen/temp/only_price_district.csv". 


#### Price difference
Price difference is a numeric variable. Represents the price difference between December 2020 and May 2021 per night in dollars.

```{r, echo = FALSE}
complete_price_comparison<- read_csv("../gen/temp/complete_price_comparison.csv")
summary(complete_price_comparison)
```
```{r, echo = FALSE}
only_price_district<- read_csv("../gen/temp/only_price_district.csv")
summary(only_price_district)
```



#### Summary Stats
#### Mean Plots
```{r, echo = FALSE, fig.align='center', out.height='40%'}
knitr::include_graphics('../../gen/output/meanplot_pricedif_district.pdf')
```

#### Box Plots
```{r, echo = FALSE, fig.align='center', out.height='40%'}
knitr::include_graphics('../../gen/output/boxplot_pricedif_district_filtered.pdf')
```

#### ANOVA Tukey Plot Table
```{r, echo = FALSE}
tukey.plot.aov <- read_csv('../../gen/output/tukey.plot.aov.csv')
```

#### ANOVA Tukey Plot Graph
```{r, echo = FALSE, fig.align='center', out.height='40%'}
knitr::include_graphics('../../gen/output/tukey.plot.test.pdf')
```








